### 2024-06-04 Manuscript/CoverLetter.tex
Update CoverLetter.tex

Since the seminal publication by Petchey and Gaston in Ecology Letters in 2002 on functional diversity (``Functional diversity (FD), species richness and community composition''; cumulating $>$ 2000 citations), functional diversity is now routinely used as a statistic to describe complex multidimensional datasets.
This has been driven by a really motivated community of ecologists proposing many different ways to measure functional diversity depending on different datasets or different questions.
More than 20 years later however, despite the enthusiasm of the ecology and evolution community there is no consensual way on which metric to use and in which scenarios they perform better.
This has led to the positive and rich paradigm of a diverse number of metrics routinely used for different tasks.

However, this richness of ways to measure functional diversity can make it daunting and or confusing for researchers that want to add functional diversity to their research methodology toolkit.
We argue that this confusions can stem from both an epistemological misunderstanding as well as practical hurdles.
The second is nicely alleviated by a dynamic community of researchers proposing open source and easy to use implementations to measure functional diveristy.
But the first hurdle remains.
Indeed, although it is often rather clear how functional diversity in general can capture changes communities (investigating processes; answering the question ``how are communities changing?'') and relate them to general understanding in ecology (understanding mechanisms; ``why are communities changing?''); surprisingly little work has been published in the last few years on how the metrics used to measure functional diversity can accurately measure complex multidimensional patterns (capturing patterns; ``what is changing?'').

>>>>

Since the seminal publication by Petchey and Gaston in Ecology Letters in 2002 \textit{``Functional diversity (FD), species richness and community composition''} (cumulating $>$ 2000 citations), functional diversity is now routinely used as a statistic to describe complex multidimensional datasets.
This has been driven by a really motivated community of ecologists proposing many different ways to measure functional diversity depending on different datasets or different questions.
More than 20 years later however, despite the enthusiasm of the ecology and evolution community there is no consensual way on which metric to use and in which scenarios they perform better.
This has led to the positive and rich paradigm of a diverse number of metrics routinely used for different tasks.

However, this richness of ways to measure functional diversity can make it daunting and or confusing for researchers that want to add functional diversity to their research methodology toolkit.
We argue that this confusions can stem from both (1) an epistemological misunderstanding as well as (2) practical hurdles.
The latter is nicely alleviated by a dynamic community of researchers proposing open source and easy to use implementations to measure functional diveristy.
But the former misunderstanding remains.
Indeed, although it is often rather clear how functional diversity in general can capture changes communities (investigating processes; answering the question ``how are communities changing?'') and relate them to general understanding in ecology (understanding mechanisms; ``why are communities changing?''); surprisingly little work has been published in the last few years on how the metrics used to measure functional diversity can accurately measure complex multidimensional patterns (capturing patterns; ``what is changing?'').
